Equalizer 2.0 --\\Convergence of a Parallel Rendering Framework

### 2018-02-08 paperIEEE.tex
removed fixmes
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@121 db7c848b-7755-4df2-b763-8796797afa52

\begin{figure}[ht]\center
  \includegraphics[width=.9\columnwidth]{images/benchmark_eqPly2}
  \caption{\label{fBenchmarkEqPly} David alley with 30 statues of 56m triangles (988\,MB) each.\FIXME{check the triangle count}}
\end{figure}

@@

The volume data sets are distributed in a single object, serializing the raw
volume buffer. The Spike volume data set has a significant compression ratio,
which is reflected by the results in \fig{fSpikesDist}. Compression for this
data is beneficial for transmitting data over a 10~Gb/s \FIXME{~10\,Gb/s ?} link even for a single
slave process. Buffering has little benefit since the serialization of volume
data is trivial. Buffered compression makes a significant difference, since the
compression cost can be amortized over $n$ nodes, reaching raw data transmission
rates of 3.7~GB/s \FIXME{~3.7\,GB/s ?} with the default Snappy compressor and at best 4.4~GB/s \FIXME{~4.4\,GB/s ?} with
ZStandard at level 1.

>>>>

\begin{figure}[ht]\center
  \includegraphics[width=.9\columnwidth]{images/benchmark_eqPly2}
  \caption{\label{fBenchmarkEqPly} David alley with 30 statues of 56\,M triangles (988\,MB) each.
\end{figure}

@@

The volume data sets are distributed in a single object, serializing the raw
volume buffer. The Spike volume data set has a significant compression ratio,
which is reflected by the results in \fig{fSpikesDist}. Compression for this
data is beneficial for transmitting data over a 10\,Gb/s link even for a single
slave process. Buffering has little benefit since the serialization of volume
data is trivial. Buffered compression makes a significant difference, since the
compression cost can be amortized over $n$ nodes, reaching raw data transmission
rates of 3.7\,GB/s with the default Snappy compressor and at best 4.4\,GB/s with
ZStandard at level 1.
